testtreefallposition

### 2021-08-18 R/DESIGNATION_DRAFT.Rmd
felling1tree test

  sp::proj4string(HollowTreescoord) <- raster::crs(DEM) # attribuer le crs de Paracou à notre inventaire spatialisé

@@

sp::proj4string(HarvestableTreesPoints) <- raster::crs(DEM)

>>>>

  sp::proj4string(HollowTreescoord) <- raster::crs(topography) # attribuer le crs de Paracou à notre inventaire spatialisé

@@

sp::proj4string(HarvestableTreesPoints) <- raster::crs(topography)

### 2021-08-18 R/Draft_spatio.Rmd
felling1tree test

---
title: "Draft_spatio"
author: "Vincyane Badouard"
date: "13/07/2021"
output: html_document
---
```{r}
inventory = ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016))))

#Taf de l'utilisateur
## Import du MNT de Paracou (1m de résolution, campagne LiDAR de 2016) ----
DemParacou <- raster::raster("D:/VSC Kourou/DATA/GIS/Topo_P6_PARACOU.tif") # MNT (altitude)
plot(DemParacou)
usethis::use_data(DemParacou)

@@

```
```{r}
# Fourni par le module de def d'UP
PlotTopo <- raster::mask(x = DemParacou, # DEM en shapefile
                         mask = Plots) # découpage de la topo par l'emprise du plot
plot(PlotTopo)
usethis::use_data(PlotTopo)

@@

proj4string(SpatInventory) <- raster::crs(DemParacou) # attribuer le crs de Paracou à notre inventaire spatialisé

@@

    distSp <- topoDist(DEM = PlotTopo, pts = SpatInventorytmp) # calcul des distances
    distSp <- as_tibble(distSp)
    distSp[distSp == 0] <- NA # ne pas prendre en compte les 0 dans la matrice, qui sont les dist de l'arbre à lui-même.
    distSp[distSp == Inf] <- NA # ne pas prendre en compte les Inf qui sont les arbres hors de parcelle.

@@

summary(SlopeCritInventory)
test_inventory <- test$inventory
coordinates(test_inventory) <- ~ Xutm + Yutm
proj4string(test_inventory) <- raster::crs(DemParacou)
test_inventory <- st_as_sf(test_inventory)

>>>>

---
title: "Draft_spatio"
author: "Vincyane Badouard"
date: "13/07/2021"
output: html_document
---
```{r}
inventory = ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016)))

#Taf de l'utilisateur
## Import du MNT de Paracou (1m de résolution, campagne LiDAR de 2016) ----
DTMParacou <- raster::raster("D:/VSC Kourou/DATA/GIS/Topo_P6_PARACOU.tif") # MNT (altitude)
plot(DTMParacou)
usethis::use_data(DTMParacou)
overwrite = TRUE

@@

```
```{r}
# Fourni par le module de def d'UP
PlotTopo <- raster::mask(x = DTMParacou, # topography en shapefile
                         mask = Plots) # découpage de la topo par l'emprise du plot
plot(PlotTopo)
usethis::use_data(PlotTopo)

@@

proj4string(SpatInventory) <- raster::crs(DTMParacou) # attribuer le crs de Paracou à notre inventaire spatialisé

@@

    distSp <- topoDist(topography = PlotTopo, pts = SpatInventorytmp) # calcul des distances
    distSp <- as_tibble(distSp)
    distSp[distSp == 0] <- NA # ne pas prendre en compte les 0 dans la matrice, qui sont les dist de l'arbre à lui-même.
    distSp[distSp == Inf] <- NA # ne pas prendre en compte les Inf qui sont les arbres hors de parcelle.

@@

summary(SlopeCritInventory)
test_inventory <- test$inventory
coordinates(test_inventory) <- ~ Xutm + Yutm
proj4string(test_inventory) <- raster::crs(DTMParacou)
test_inventory <- st_as_sf(test_inventory)

### 2021-08-18 R/TreeFelling_Draft.Rmd
felling1tree test

```{r Give values to the arguments to work}
data(Paracou6_2016)
data(DemParacou)

@@

inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
                           objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
                           advancedloggingparameters = loggingparameters())$inventory

@@

speciescriteria = SpeciesCriteria
scenario = "manual"
fuel = "2"
objective = 20
diversification = TRUE
directionalfelling = "2"
specieslax = FALSE
objectivelax = FALSE
DEM = DemParacou
advancedloggingparameters = loggingparameters()
# MainTrail

@@

# sp::coordinates(SelectedTrees) <- ~ Xutm + Yutm
# 
# sp::proj4string(SelectedTrees) <- raster::crs(DEM)
# 
# SelectedTrees <- st_as_sf(as(SelectedTrees,"SpatialPoints"))

>>>>

```{r Give values to the arguments to work}
data(Paracou6_2016)
data(DTMParacou)

@@

inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
                           objectivelax = FALSE, topography = DTMParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
                           advancedloggingparameters = loggingparameters())$inventory

@@

speciescriteria = SpeciesCriteria
scenario = "manual"
fuel = "2"
objective = 20
diversification = TRUE
directionalfelling = "2"
specieslax = FALSE
objectivelax = FALSE
topography = DTMParacou
advancedloggingparameters = loggingparameters()
# MainTrail

@@

# sp::coordinates(SelectedTrees) <- ~ Xutm + Yutm
# 
# sp::proj4string(SelectedTrees) <- raster::crs(topography)
# 
# SelectedTrees <- st_as_sf(as(SelectedTrees,"SpatialPoints"))

### 2021-08-18 R/TreeFelling_Draft2.Rmd
Corrections (cleaninventory)
felling1tree test

# INPUTS
```{r Give values to the arguments to work}
data(Paracou6_2016)
data(DemParacou)

inventory <- addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016)))

inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
                           objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
                           advancedloggingparameters = loggingparameters())$inventory

speciescriteria = SpeciesCriteria
scenario = "manual"
fuel = "2"
objective = 20
diversification = TRUE
directionalfelling = "2"
specieslax = FALSE
objectivelax = FALSE
DEM = DemParacou
advancedloggingparameters = loggingparameters()
# MainTrail

>>>>

# INPUTS
```{r Give values to the arguments to work}
data(Paracou6_2016)
data(DTMParacou)

inventory <- addtreedim(inventorycheckformat(Paracou6_2016)))

inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
                           objectivelax = FALSE, topography = DTMParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
                           advancedloggingparameters = loggingparameters())$inventory

speciescriteria = SpeciesCriteria
scenario = "manual"
fuel = "2"
objective = 20
diversification = TRUE
directionalfelling = "2"
specieslax = FALSE
objectivelax = FALSE
topography = DTMParacou
advancedloggingparameters = loggingparameters()
# MainTrail

### 2021-08-18 R/Treefelling_Sylvain's version.Rmd
felling1tree test

inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
                           objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
                           advancedloggingparameters = loggingparameters())$inventory
```

@@

```{r}
st_tree <- function(dat,
                    ScndTrail = ScndTrail,
                    MainTrail = MainTrail,
                    fuel, 
                    directionalfelling, 
                    advancedloggingparameters = loggingparameters()){

@@

# To extract de the shortest ways
NearestPoints <- SelectedTrees %>%
  group_by(idTree) %>% 
  do(geometry = st_tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$NearestPoints) %>% 
  mutate(geometry = as(geometry, "sfc_LINESTRING")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf()

# Application in a dataframe
FellingTrees <- SelectedTrees %>% 
  # mutate(angle = list(c(0, 30))) %>% # for each row, a list of 2 values -> a dataframe in a dataframe
  # unnest(angle) %>% # display the small dataframe in the big dataframe in one
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry = st_tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$A) %>% # inform geometry. # Filling a column from a function whose input is a table

  # or version more Sf (to test)
  # pol <- st_as_sf(SelectedTrees, 
  #                 as(geometry = st_as_sfc(
  #                   lapply(split(SelectedTrees, SelectedTrees$idTree), st_tree(30))
  #                 )
  #                 , "sfc_MULTIPOLYGON")
  # )

@@

FellingTrees <- inventory %>% 
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
       ifelse(!is.na(.$TreeFellingOrientationSuccess),
              st_tree(.,
                      ScndTrail = ScndTrail,
                      MainTrail = MainTrail,
                      fuel = "2", directionalfelling ="2",
                      advancedloggingparameters = loggingparameters())$A,
              NULL)) %>%
  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf()

felttress <- NA
inventory %>% 
  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
       st_tree(.,
               ScndTrail = ScndTrail,
               MainTrail = MainTrail,
               fuel = "2", directionalfelling = "2",
               advancedloggingparameters = loggingparameters())$A) %>%
  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf() %>% 
  mutate(geometry = st_as_text(geometry))

@@

felttrees <- inventory %>% 
  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
  st_tree(.,
          ScndTrail = ScndTrail,
          MainTrail = MainTrail,
          fuel = "2", directionalfelling = "2",
          advancedloggingparameters = loggingparameters())$A %>% 
  st_as_text()  # as text to easy join with a non spacial table
# unnest(treepolygon) # display the small dataframe in the big dataframe in one

@@

# Treefelling
felttrees <- inventory %>%
  filter(!is.na(TreeFellingOrientationSuccess)) %>%
  group_by(idTree) %>% # for each tree
  do(TreePolygon = # inform geometry. # Filling a column from a function whose input is a table
       st_tree(.,
               fuel = "2", directionalfelling = "2",
               MainTrail = MainTrail, ScndTrail = ScndTrail,
               advancedloggingparameters = loggingparameters())$A %>%
       st_as_text()) %>% # as text to easy join with a non spacial table
  tidyr::unnest(TreePolygon) # here to pass from list to character

>>>>

inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
                           objectivelax = FALSE, topography = DTMParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
                           advancedloggingparameters = loggingparameters())$inventory
```

@@

```{r}
felling1tree <- function(dat,
                    ScndTrail = ScndTrail,
                    MainTrail = MainTrail,
                    fuel, 
                    directionalfelling, 
                    advancedloggingparameters = loggingparameters()){

@@

# To extract de the shortest ways
NearestPoints <- SelectedTrees %>%
  group_by(idTree) %>% 
  do(geometry = felling1tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$NearestPoints) %>% 
  mutate(geometry = as(geometry, "sfc_LINESTRING")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf()

# Application in a dataframe
FellingTrees <- SelectedTrees %>% 
  # mutate(angle = list(c(0, 30))) %>% # for each row, a list of 2 values -> a dataframe in a dataframe
  # unnest(angle) %>% # display the small dataframe in the big dataframe in one
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry = felling1tree(., ScndTrail = ScndTrail, MainTrail = MainTrail, fuel = "2", directionalfelling ="2", advancedloggingparameters = loggingparameters())$A) %>% # inform geometry. # Filling a column from a function whose input is a table

  # or version more Sf (to test)
  # pol <- st_as_sf(SelectedTrees, 
  #                 as(geometry = st_as_sfc(
  #                   lapply(split(SelectedTrees, SelectedTrees$idTree), felling1tree(30))
  #                 )
  #                 , "sfc_MULTIPOLYGON")
  # )

@@

FellingTrees <- inventory %>% 
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
       ifelse(!is.na(.$TreeFellingOrientationSuccess),
              felling1tree(.,
                      ScndTrail = ScndTrail,
                      MainTrail = MainTrail,
                      fuel = "2", directionalfelling ="2",
                      advancedloggingparameters = loggingparameters())$A,
              NULL)) %>%
  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf()

felttress <- NA
inventory %>% 
  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
  group_by(idTree) %>% # for each tree and each given angle 
  do(geometry =  # inform geometry. # Filling a column from a function whose input is a table
       felling1tree(.,
               ScndTrail = ScndTrail,
               MainTrail = MainTrail,
               fuel = "2", directionalfelling = "2",
               advancedloggingparameters = loggingparameters())$A) %>%
  mutate(geometry = as(geometry, "sfc_MULTIPOLYGON")) %>% # list -> sfc_MULTIPOLYGON
  st_as_sf() %>% 
  mutate(geometry = st_as_text(geometry))

@@

felttrees <- inventory %>% 
  filter(!is.na(TreeFellingOrientationSuccess)) %>% 
  felling1tree(.,
          ScndTrail = ScndTrail,
          MainTrail = MainTrail,
          fuel = "2", directionalfelling = "2",
          advancedloggingparameters = loggingparameters())$A %>% 
  st_as_text()  # as text to easy join with a non spacial table
# unnest(treepolygon) # display the small dataframe in the big dataframe in one

@@

# Treefelling
felttrees <- inventory %>%
  filter(!is.na(TreeFellingOrientationSuccess)) %>%
  group_by(idTree) %>% # for each tree
  do(TreePolygon = # inform geometry. # Filling a column from a function whose input is a table
       felling1tree(.,
               fuel = "2", directionalfelling = "2",
               MainTrail = MainTrail, ScndTrail = ScndTrail,
               advancedloggingparameters = loggingparameters())$A %>%
       st_as_text()) %>% # as text to easy join with a non spacial table
  tidyr::unnest(TreePolygon) # here to pass from list to character

### 2021-08-18 R/Treefelling_test_for all trees.Rmd
felling1tree test

inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
                           objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
                           advancedloggingparameters = loggingparameters())$inventory

speciescriteria = SpeciesCriteria
scenario = "manual"
fuel = "2"
objective = 20
diversification = TRUE
directionalfelling = "2"
specieslax = FALSE
objectivelax = FALSE
DEM = DemParacou
advancedloggingparameters = loggingparameters()
# MainTrail

>>>>

inventory <- treeselection(inventory, objective = 20, scenario ="manual", fuel = "2", diversification = TRUE, specieslax = FALSE,
                           objectivelax = FALSE, topography = DTMParacou, plotslope = PlotSlope, speciescriteria = SpeciesCriteria,
                           advancedloggingparameters = loggingparameters())$inventory

speciescriteria = SpeciesCriteria
scenario = "manual"
fuel = "2"
objective = 20
diversification = TRUE
directionalfelling = "2"
specieslax = FALSE
objectivelax = FALSE
topography = DTMParacou
advancedloggingparameters = loggingparameters()
# MainTrail

### 2021-08-18 R/testtreefallposition.Rmd
felling1tree test

inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
inventory <- suppressMessages(treeselection(inventory, objective = 30, scenario ="manual",
                                            fuel = "2", diversification = TRUE, specieslax = FALSE,
                                            objectivelax = FALSE, DEM = DemParacou, plotslope = PlotSlope,
                                            speciescriteria = SpeciesCriteria,
                                            advancedloggingparameters = loggingparameters())$inventory)
```

>>>>

inventory <- addtreedim(inventorycheckformat(Paracou6_2016))
inventory <- suppressMessages(treeselection(inventory, objective = 30, scenario ="manual",
                                            fuel = "2", diversification = TRUE, specieslax = FALSE,
                                            objectivelax = FALSE, topography = DTMParacou, plotslope = PlotSlope,
                                            speciescriteria = SpeciesCriteria,
                                            advancedloggingparameters = loggingparameters())$inventory)
```
